### 2020-06-21 chapters/my-work.tex
Why we build divergence distribution

To compare each feature's reference and sliding window histogram aggregation we need a measure of divergence. We chose to use the Jensen–Shannon Divergence (JSD) \cite{JSD} but other statistical tests are possible such as Kolmogorov-Smirnov or Wasserstein. A more thorough analysis on some statistical tests and why we chose to use the JSD is performed in Section \ref{sec:whyjsds}. Given a divergence value for the two aggregations (reference and sliding window ones) we need a measure of normal statistical fluctuations. Since we assume a reference period as the normal state we can find out the normal distribution for the divergence by sampling smaller windows of data from the reference period in a batch analysis. This allows us to define a threshold based on percentiles, which gives an estimate for the probability of a certain value occurring, rather than using a constant hand picked threshold for the divergence value. \textcolor{red}{defer details to later section}

@@

\iffalse
\subsection*{Defining the deviation threshold}
Assume we use a distance function that takes two histograms --- our reference aggregation histogram and our sliding window aggregation histogram --- and outputs a distance value. How do we threshold this value? For instance, consider the following left and right-skewed distance distributions represented by Figures \ref{fig:skewed-left-distro} and \ref{fig:skewed-right-distro}, respectively. Note that these histograms do not represent the reference and/or sliding window aggregation histograms. Here we make the assumption we have a histogram that encodes the distribution of distance values measured between the reference aggregation and the sliding window aggregation.

Hard-coding a threshold value to be used for all features is cumbersome, impractical and error-prone. The distance threshold must be computed based on the distribution of distances. How do we get to know the distribution of such distances? That is one of the goals of the batch phase.
\fi

@@

\subsubsection*{Finding the distribution of distances for each feature} \label{sec:sampling-batch}
Secondly, we aim to build the histogram that encodes the distribution of expected distance values, to later on threshold the observed distance values during the online phase. To that end, we make \textit{S} samples of transactions, each with the same tuple-based size of the sliding window we will use in streaming. Each sample is a contiguous block of transactions, thus preserving the order of transactions and the time-dependency property of a time-series.

@@

>>>>

To compare each feature's reference and sliding window histogram aggregation we need a measure of divergence. We chose to use the Jensen–Shannon Divergence (JSD) \cite{JSD} but other statistical tests are possible such as Kolmogorov-Smirnov or Wasserstein. A more thorough analysis on some statistical tests and why we chose to use the JSD is performed in Section \ref{sec:whyjsds}. Given a divergence value for the two aggregations (reference and sliding window ones) we need a measure of normal statistical fluctuations. Since we assume a reference period as the normal state we can find out the normal distribution for the divergence by sampling smaller windows of data from the reference period in a batch analysis. This allows us to define a threshold based on percentiles, which gives an estimate for the probability of a certain value occurring, rather than using a constant hand picked threshold for the divergence value (details in Section \ref{sec:sampling-batch}).

@@

@@

\subsubsection*{Finding the distribution of distances for each feature} \label{sec:sampling-batch}

Secondly, we aim to build the histogram that encodes the distribution of expected distance values, to later on threshold the observed distance values during the online phase. To that end, we make \textit{S} samples of transactions, each with the same tuple-based size of the sliding window we will use in streaming. Each sample is a contiguous block of transactions, thus preserving the order of transactions and the time-dependency property of a time-series.

@@

It is important to understand why we want to know the distribution of divergence values instead of just thresholding the divergence value itself. For instance, given the JSD value varies between 0 and 1, why not just set to alert if the measured JSD value is 0.7? The reason is that a divergence value may fall on different percentiles for different features. In other words, the same \textit{i-th} percentile will correspond to a different divergence value for different features. Consider the following left and right-skewed distance distributions represented by Figures \ref{fig:skewed-left-distro} and \ref{fig:skewed-right-distro}, respectively.

Hard-coding a threshold value to be used for all features is cumbersome, impractical and error-prone. The distance threshold must be computed based on the distribution of distances.
